The Forward March of Categorical Tolerance in the United States\thanks{Reserved for acknowledgments}

### 2025-06-08 manuscript.tex
Updates from Overleaf

>>>>

\begin{table}
    \caption{Coefficient Estimates from Zero-Inflated Poisson Models Predicting Categorical Tolerance and Symbolic Exclusion, Joint Prolific and Lucid Samples.}
    \centering
    \includegraphics[trim={0 3cm 11.6cm 0},clip, width=1.0\textwidth]{Tabs/zinf-reg.png}
    \label{tab:zinf}
\end{table}

Table~\ref{tab:zinf} shows the coefficient estimates from a set of four zero-inflated Poisson regression models. The specifications in each model, for both the count and zero-inflated components, are informed by the descriptive patterns we considered in Figures~\ref{fig:cat-tol} and~\ref{fig:grd-int}. Coefficient estimates corresponding to the count part of the model---predicting the number of dislikes among those who are at risk of expressing them---are shown in the top half of the table. Coefficient estimates for the zero-inflation part of the model, predicting the odds of landing in the categorical tolerant group---and thus not being at risk of engaging in symbolic exclusion---are presented in the lower half of the table. In all models, age, education, income, and political ideology (with higher values indicating a more liberal stance) are entered as ordered numerical inputs. Race (White) and Gender (Female) are entered into the model as dummy indicators. The zero-inflated specifications also contain squared terms for education and income to model expected curvilinear effects (see Figures~\ref{fig:cat-tol-edu} and~\ref{fig:cat-tol-inc}).

Let us begin with the predictors of symbolic exclusion;
